---
title: "Simulation Exercise: Investigate the exponential distribution in R and compare it with the Central Limit Theorem."
author: "Leena Sonpethkar"
date: "October 8, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
The purpose of this simulation exercise is to investigate the exponential distribution and compare it to the Central Limit Theorem.
This exercise will investigate the distribution of averages of 40 exponentials over thousand simulations.
In this exercise, the lambda will be set to 0.2 for all of the simulations. 

## Simulations
The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. 
The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. 
lambda will be set to 0.2 for all of the simulations. This simulation will help to investigate the distribution of averages of 40 exponential(0.2)s. Note that you will need to do a thousand or so simulated averages of 40 exponentials.

###Set all the variables

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
