---
title: "Simulation Exercise: Investigate the exponential distribution in R and compare it with the Central Limit Theorem."
author: "Leena Sonpethkar"
date: "October 8, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Overview
The purpose of this simulation exercise is to investigate the exponential distribution and compare it to the Central Limit Theorem.
This exercise will investigate the distribution of averages of 40 exponentials over thousand simulations.
In this exercise, the lambda will be set to 0.2 for all of the simulations. 

## 2.Simulations
The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. 
The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. 
lambda will be set to 0.2 for all of the simulations. 

###Set all the variables
```{r, echo=TRUE}
set.seed(20201008)
lambda <- 0.2
nExp <- 40
nSamples <- 1000
```

### Run simulations
```{r, echo=TRUE}
simulated_sample <- replicate(nSamples, rexp(nExp, lambda))
simMean <- apply(simulated_sample, 2, mean)
```

## 3.Compare Sample Mean versus Theoretical Mean

```{r, echo=TRUE}
#Calculate Sample Mean
sample_mean <- mean(simMean)

#Calculate Theoretical Mean
theo_mean <- 1 / lambda
```

### Mean Comparison
```{r, echo=TRUE}
diff_mean <- abs(sample_mean-theo_mean)
diff_mean
```
The mean of the sample means is  0.05248837 and the theoritical mean is 5. 
The sample mean and the theoretical mean (expected mean) are very close.

## 4.Compare Variance
```{r, echo=TRUE}
#Calculate Sample Variance & Standard deviation
sample_var <- var(simMean)
sample_sd <- sd(simMean)
#Calculate Theoretical Variance & Standard deviation
theo_var  <- (1 / lambda)^2 / (nExp) 
theo_sd  <- 1/(lambda * sqrt(nExp))
```
The variance of sample means is `r sample_var` and theoretical variance is `r theo_var`. Both these variances are found to close to each other.
While Standard deviation of sample means is `r sample_sd` and theoretical standard deviation is `r theo_sd`. Again both standard deviations are found to close to each other.

## 5.Distribution
```{r} 
library(ggplot2) 
histdata <- data.frame(simMean)
m <- ggplot(histdata, aes(x =simMean))
m <- m + geom_histogram(aes(y=..density..), binwidth = 0.2, colour="grey",
                        fill = "grey66")
m <- m + labs(title = "Means Distribution of 40 Samples", x = "Mean of 40 Samples", y = "Density")
m <- m + geom_vline(aes(xintercept = sample_mean, colour = "sample"))
m <- m + geom_vline(aes(xintercept = theo_mean, colour = "theoretical"))
m <- m + stat_function(fun = dnorm, args = list(mean = sample_mean, sd = sample_sd), color = "dark blue", size = 1.5)
m <- m + stat_function(fun = dnorm, args = list(mean = theo_mean, sd = theo_sd), colour = "red", size = 1.5)
m





```


